---
title: "Summary"
author: "Tilen Gimpelj, Maja Kovač"
date: "`r date()`"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: TRUE
    code_folding: hide
bibliography: reference.bib
link-citations: yes
csl: ieee-with-url.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,include=T,error=F,warning = F,message=F)
pkgs <- c("rlang","tidyverse","readxl","writexl","lubridate","stringr","esquisse","miniUI","pheatmap","RColorBrewer","hexbin","BiocManager","reshape2","ggnewscale","ggbeeswarm","kableExtra", "DT")
bioc_pkgs <- c("DESeq2","SummarizedExperiment","GEOquery","biomaRt","org.Hs.eg.db","org.Mm.eg.db","pathview","clusterProfiler","EnhancedVolcano","apeglm","genefilter","tximport","tximeta","GenomicFeatures","edgeR","SBGNview")

for (pkg in pkgs) {if (pkg %in% installed.packages()) {message(pkg," installed, loading...");library(pkg,character.only = T)} else {message(pkg," not instlled, installing...");install.packages(pkg,dependencies =T,quiet = T)}}
bmngr<-"BiocManager";
if (bmngr %in% installed.packages()) {library(bmngr,character.only = T)} else {install.packages(bmngr,dependencies =T,quiet = T)}
for (bpkg in bioc_pkgs) {if (bpkg %in% installed.packages()) {message(bpkg," installed, loading...");library(bpkg,character.only = T)} else {message(bpkg," not instlled, installing...");BiocManager::install(bpkg,update=T,ask=F)}}
```

<p><a class="btn btn-primary" data-toggle="collapse" href="#collapseExample1" role="button" aria-expanded="false" aria-controls="collapseExample1"> Environment </a></p>

::: {#collapseExample1 .collapse}
::: {.card .card-body}
```{r, results='asis',echo=FALSE}
info <- sessionInfo()
datatable(data.frame(version = sapply(info$otherPkgs,FUN = \(x) {c(x$package,x$Version)}),
                        "Package_Manager" = sapply(info$otherPkgs,FUN = \(x){if (x$Package %in% bioc_pkgs){"BiocManager"} else {""}})),
          caption = info$R.version$version.string)
```
:::
:::

# Summary

Researchers conducted a study to demonstrate the importance of reporting dietary conditions in mouse studies. Lgr5^EGFP-cre:ERT2^ mice were fed different diets from weaning. The diets differed in many nutrient levels. These included 4 diets:

1)  diet: high-fat purified diet in which 60% of calories are from fat (HFD)
2)  diet: a chow diet often used as a control
3)  diet: a purified diet that is a specific control for the purified HFD with 10% calories from fat, 20% protein, 70% carbohydrates (HFcontrol)
4)  diet: another purified diet AIN76A

The high-fat diet group were female mice. The chow cohort consisted of male mice. The purified control diet cohorts were mixed group of female and male mice.

Mice were sacrificed at 3 months. Lgr5hi cells were then collected by FACS from isolated intestinal crypts, and their RNA was harvested and subjected to RNA-seq.

The study found that the chow-fed mice had different gene expression patterns compared to those fed purified diets. The different diets had varying nutrient levels, and the chow diet contained high phytoestrogen levels, which could affect stem cell function.

Dietary effects can ripple through layers of biochemical, signaling, metabolic, and epigenetic regulation, and therefore purified diets should be used for experimental animals, avoiding potential complications from chow diets.

The choice of diet used in rodent studies is important and depends on the research question. Specifics of the diet should be provided in a transparent format to promote data reproducibility and interpretation. Purified diets are recommended to avoid potential complications from chow diets and to better isolate the effects of specific nutrients. The choice of diet used in mouse experiments should be carefully considered, and dietary information should be reported clearly in rodent studies.

This established that intestinal stem/ progenitor-like cell function can be recruited by the nutritional environment, not only by damage or genetic manipulation of Lgr5hi cells.

A mouse diet that mimics the nutrient levels in human diets and is linked to high colon cancer risk causes tumors in mouse intestines and affects the function of intestinal stem cells. This shows that the nutritional environment can influence stem cell function, not just genetic or physical damage.

All this emphasizes the importance of choosing diets carefully for mouse experiments and reporting dietary information clearly in stem cell-based and other rodent studies. [@2020]

------------------------------------------------------------------------

# Preparation of data

```{r}
GEOaccN <- "GSE151498"
```

Geo Access number: `r GEOaccN`

## Basic info

```{r}
gse1 <- getGEO(GEOaccN,GSEMatrix =TRUE)[[1]]
se1 <- as(gse1, "SummarizedExperiment")
if (!(GEOaccN %in% list.files())){ getGEOSuppFiles(GEOaccN)}

files <- list.files(GEOaccN,full.names=T)
read.table(files[1], skip=0, sep = "\t", header=TRUE) -> df1 #, row.names = 1)
read.table(files[2], skip=0, sep = "\t", header=TRUE) %>%  
  rename("ensemblID"= "geneNames") %>% 
  full_join(df1 %>% 
       select(geneNames,ensemblID)) %>% 
  relocate(geneNames)-> df2#, row.names = 2)

```

<p><a class="btn btn-primary" data-toggle="collapse" href="#collapseExample3" role="button" aria-expanded="false" aria-controls="collapseExample3"> Datasets </a></p>

::: {#collapseExample3 .collapse}
::: {.card .card-body}
**Dataset 1**

```{r}
datatable(df1)
```

**Dataset 2**

```{r}
datatable(df2)
```
:::
:::

<p><a class="btn btn-primary" data-toggle="collapse" href="#collapseExample2" role="button" aria-expanded="false" aria-controls="collapseExample2"> Genes </a></p>

::: {#collapseExample2 .collapse}
::: {.card .card-body}
**Genes in the dataset:**

```{r}
df1 %>%  
  group_by(geneNames) %>% 
  dplyr::count(geneNames)  %>% 
  rename(count = n, "Gene Name" = geneNames) %>% 
  datatable()  

```
:::
:::

------------------------------------------------------------------------

## Design of the experiment

The experiment was conducted on *Lgr5^EGFP-cre:ERT2^* mice that were feed different diets. These included a high-fat purified diet in which 60% of calories are from fat [@2016], a chow diet (PicoLab 5058, LabDiets) often used as a control and which was compared to the purified HFD in Beyaz et al., a purified diet that is a specific control for the purified HFD with 10% calories from fat (HFcontrol, Research Diets, 12450B), and another purified diet, AIN76A (Research Diets, D10001). The diets differed in many nutrient levels, and importantly the chow but not purified diets contained high phytoestrogen levels. After 3 months, Lgr5^hi^ cells were collected by FACS from isolated intestinal crypts, and their RNA was harvested and subjected to RNA-seq [@2019].

```{r data-preparation}
df1 %>% 
  group_by(geneNames) %>% 
  summarise_if(is.numeric, sum) %>% 
  as.data.frame -> df1a

df1a %>% 
  column_to_rownames(var = "geneNames") -> df1b

rownames(se1@colData)<-colnames(df1b)
df1b %>% 
  mutate_if(is.numeric,round) -> df1b

se1@colData$diet.ch1 <- factor(
  str_replace(
    str_replace(
        str_extract(se1@colData$diet.ch1,
                    "[A-Za-z 0-9]*"),
      " $",
      ""),
    " ",
    "_"))

se1@colData$gender.ch1 <- factor(se1@colData$gender.ch1)

dds_diet <- DESeqDataSetFromMatrix(countData = df1b,
                                     colData = se1@colData,
                                     design = ~ diet.ch1,
                                     metadata = metadata(se1))
dds_sex <- DESeqDataSetFromMatrix(countData = df1b,
                                     colData = se1@colData,
                                     design = ~ gender.ch1,
                                     metadata = metadata(se1))
dds_sex_p_diet <- DESeqDataSetFromMatrix(countData = df1b,
                                     colData = se1@colData,
                                     design = ~ gender.ch1 + diet.ch1,
                                     metadata = metadata(se1))

saveRDS(
  list("diet" = dds_diet,
       "sex_p_diet" = dds_sex_p_diet,
       "sex" = dds_sex),
  file = "data.rds")


```

# Analysis

In the analysis we comapred diet groups `chow` and `AI76A`.

## Exploratory analysis and visualisation

```{r}
dds_diet_filtered <- dds_diet[rowSums(counts(dds_diet)) > 1,]

vst_diet <- vst(dds_diet_filtered, blind = F)
rld_diet <- rlog(dds_diet_filtered, blind = F)

dds_diet_est_factors <- estimateSizeFactors(dds_diet)

dds_diet_dataframe <- as.data.frame(log2(counts(dds_diet_est_factors,
                                                normalized = TRUE)[,1:2]+1)) %>% 
  mutate(transformation = "log2(x + 1)") %>% 
  bind_rows(as_data_frame(assay(vst_diet)[, 1:2]) %>% mutate(transformation = "vst"),
            as_data_frame(assay(rld_diet)[, 1:2]) %>% mutate(transformation = "rlog"))

colnames(dds_diet_dataframe)[1:2] <- c("x","y")

dds_diet_dataframe_levels <- c("log2(x + 1)", "vst", "rlog")
dds_diet_dataframe$transformation <- factor(dds_diet_dataframe$transformation, levels = dds_diet_dataframe_levels)

```

### Plot

```{r}
ggplot(dds_diet_dataframe,
       aes(x, y)) +
  geom_hex(bins = 80) +
  coord_fixed() +
  facet_grid(. ~ transformation)
```

### Sample Distances

```{r}
vst_diet_dist_matrix <- vst_diet %>% 
  assay() %>% 
  t() %>% 
  dist() %>% 
  as.matrix()

rownames(vst_diet_dist_matrix) <- paste(vst_diet$diet.ch1)
colnames(vst_diet_dist_matrix) <- paste(vst_diet$diet.ch1)

colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
```

```{r pheatmap-dist}
pheatmap(vst_diet_dist_matrix,
         col = colors)
```

### PCA plot

```{r PCA-plot, fig.cap="PCA plot of mice diets. Chow show segregation from other groups."}
plotPCA(vst_diet, intgroup = c("diet.ch1"), returnData = T) %>% 
  ggplot(aes(x = PC1, y = PC2, color = group)) +
  geom_point() +
  geom_density2d(contour_var = "ndensity", alpha = 0.3,)
```

### MDS

```{r}
vst_diet_mds <- as.data.frame(colData(vst_diet)) %>% 
  cbind(cmdscale(vst_diet_dist_matrix))
```

```{r}
ggplot(vst_diet_mds, 
       aes(x = `1`,
           y = `2`,
           color = diet.ch1,
           shape = gender.ch1)) +
  geom_point(size = 3) + 
  coord_fixed() +
  ggtitle("MDS with VST data")
```

```{r}
ggplot(vst_diet_mds, 
       aes(x = `1`,
           y = `2`,
           color = title)) +
  geom_point(size = 3) + 
  coord_fixed() +
  ggtitle("MDS with VST data")
```

## Differential Expression Analysis

```{r}
DESeq_diet <- DESeq(dds_diet)
res_diet <- results(DESeq_diet)
res_diet_compare <- results(DESeq_diet,
                            contrast = c("diet.ch1","chow","AIN76A"))

res_diet_A.05 <- results(DESeq_diet, alpha = 0.05)
res_diet_LFC1 <- results(DESeq_diet, lfcThreshold = 1)

```

```{r}
res_diet_sig <- subset(res_diet, padj < 0.1 )
```

```{r}
topGs <- dds_diet %>% 
  DESeq() %>% 
  results() %>% 
  na.omit()  %>% 
  .[abs(.$log2FoldChange) > 0.5,] %>% 
  .[order( abs(.$log2FoldChange),decreasing = T),] %>% 
  head(20) %>% 
  rownames()

topG <- topGs[1]
topG2 <- topGs[5] # Ang4
```

### Top Genes

```{r topGenes, fig.cap="Top 20 expressed genenes arranged by descending log"}

res_diet[topGs,] %>% 
  as.data.frame() %>% 
  arrange(desc(abs(log2FoldChange))) %>% 
  mutate(Rank = 1:20) %>% 
  datatable()
```

### Count of Top Gene

#### Ang4

```{r topG-count2,  fig.cap="plot of counts for top Gene"}
plotCounts(dds_diet,
           gene = topG2,
           intgroup = c("diet.ch1"))
```

```{r topG-count-sex2, fig.cap="Plot with mice sex difference"}
plotCounts(dds_diet,
           gene = topG2,
           intgroup = c("gender.ch1"))
```

#### Pla2g4c

```{r topG-count,  fig.cap="plot of counts for top Gene"}
plotCounts(dds_diet,
           gene = topG,
           intgroup = c("diet.ch1"))
```

```{r topG-count-sex, fig.cap="Plot with mice sex difference"}
plotCounts(dds_diet,
           gene = topG,
           intgroup = c("gender.ch1"))
```

```{r}
geneCounts <- plotCounts(dds_diet,
                         gene = topG,
                         intgroup = c("diet.ch1","gender.ch1"),
                         returnData = T)
```

```{r}
ggplot(geneCounts,
       aes(x = diet.ch1,
           y = count,
           color = gender.ch1)) +
  scale_y_log10() +
  geom_beeswarm(cex = 3)
```

```{r}
ggplot(geneCounts,
       aes(x = diet.ch1,
           y = count,
           color = gender.ch1,
           group = gender.ch1)) +
  scale_y_log10() +
  geom_point(size = 3) +
  geom_line()
```

### MA plot

```{r}
n<-4
DESeq_diet_bP_f <- DESeq(dds_diet, betaPrior = F)
```

`r resultsNames(DESeq_diet_bP_f)[n]`

```{r}
# resultsNames(DESeq(dds_diet, betaPrior = F))

MA_s_p_d <- lfcShrink(DESeq_diet_bP_f,
                    coef = n, # chaw vs AIN76A
                    type = "apeglm")

DESeq2::plotMA(MA_s_p_d, ylim = c(-5, 5))
```

### gene clustering

```{r}
anno <- colData(dds_diet)[, c("diet.ch1", "gender.ch1")] %>% 
  as.data.frame()

result <- dds_diet %>% 
  DESeq() %>% 
  results() %>% 
  na.omit()  %>% 
  .[abs(.$log2FoldChange) > 0.5,] %>% 
  .[order( abs(.$log2FoldChange),decreasing = T),] %>% 
  head(20) %>% 
  rownames() %>% 
  vst_diet[.,] %>% 
  assay()
```

```{r gene-diet-matrix, fig.cap="Heatmap of genes and samples in the study"}
pheatmap(result,
         annotation_col = anno,
         fontsize_row = 5)
```

### Annotation

```{r}
dtb <- org.Mm.eg.db

sample_dtb <- sapply(columns(dtb), 
                     \(x){
                       head(keys(dtb,
                                 keytype = x),
                            3)})
head(keys(dtb, keytype = "ALIAS"), 20)
head(keys(dtb, keytype = "SYMBOL"), 20)

dds_sex_p_diet %>% 
  counts() %>% 
  rownames() %>% 
  length()


sum(rownames(counts(dds_sex_p_diet)) %in% keys(dtb,keytype="ALIAS"))
sum(rownames(counts(dds_sex_p_diet)) %in% keys(dtb,keytype="SYMBOL"))

df_anno_1 <- AnnotationDbi::select(x = dtb,
                                   keys = rownames(counts(dds_sex_p_diet)),
                                   column = c("ENSEMBL", "ENTREZID"),
                                   keytype = "SYMBOL",
                                   multiVals = "first")

df_anno_2 <- mapIds(x = dtb,
                    keys = rownames(counts(dds_sex_p_diet)),
                    column = "ENSEMBL",
                    keytype = "ALIAS",
                    multiVals = "first")

```

### Volcano plot

```{r }
df_diet <- as.data.frame(counts(dds_diet))
coldta <- colData(dds_diet)
mtadta <- metadata(dds_diet)

DESeq_diet_res_compare <- results(DESeq_diet,
             contrast = c("diet.ch1", "chow", "AIN76A"))

DESeq_diet_lfc <- lfcShrink(DESeq_diet,
                            contrast = c("diet.ch1", "chow", "AIN76A"),
                            res = DESeq_diet_res_compare,
                            type = "normal")
```

```{r volcanoplot, fig.cap="Volcano plot in contrast of chow and AIN76A feeds"}
EnhancedVolcano(DESeq_diet_lfc,
                lab = rownames(DESeq_diet_lfc),
                x = "log2FoldChange",
                y = "pvalue")
```

```{r}
ensembl <- useMart("ensembl")
datasets <- listDatasets(ensembl)

ensembl <- useDataset("mmusculus_gene_ensembl", mart = ensembl)
filters <- listFilters(ensembl)
attributes <- listAttributes(ensembl)

dbi_anno <- AnnotationDbi::select(x = dtb,
                                   keys = rownames(counts(dds_sex_p_diet)),
                                   column = c("ENTREZID","SYMBOL"),
                                   keytype = "SYMBOL",
                                   multiVals = "first")

bm_anno <- getBM(attributes=c("ensembl_gene_id","description","chromosome_name", 
                              'entrezgene_id',"uniprot_gn_symbol","hgnc_symbol"), 
                 filters = "entrezgene_id", 
                 values =  dbi_anno$ENTREZID, 
                 mart = ensembl)

bm_anno$entrezgene_id <- as.character(bm_anno$entrezgene_id)

dtb_anno <- dbi_anno %>% 
  inner_join(bm_anno, by = c("ENTREZID" = "entrezgene_id"))

dtb_df <- as.data.frame(counts(dds_sex_p_diet))
```

```{r boxplot-counts}
boxplot(x = as.list(dtb_df))
```

```{r}
ggplot(data = melt(dtb_df),
       aes(x = variable,
           y = value)) +
  geom_boxplot(aes(fill = variable))
```

```{r}
vst_s_p_d <- vst(dds_sex_p_diet)

dtb_df2 <- as.data.frame(assay(vst_s_p_d))

ggplot(data = melt(dtb_df2),
       aes(x = variable,
           y = value)) +
  geom_boxplot(aes(fill = variable))
```

```{r}
rld_sex_p_diet <- rlog(dds_sex_p_diet)

df_rlog_sex_p_diet <- as.data.frame(assay(vst_s_p_d))

ggplot(data = melt(df_rlog_sex_p_diet), 
       aes(x=variable, y=value)) + 
  geom_boxplot(aes(fill=variable))
```

## Functional enrichment analysis

### Gene ontology analysis

Gene Ontology defines concepts/classes used to describe gene function, and relationships between these concepts. It classifies functions along three aspects:

MF: Molecular Function molecular activities of gene products

CC: Cellular Component where gene products are active

BP: Biological Process pathways and larger processes made up of the activities of multiple gene products

### Encrich GO

```{r}
sig_exp_genes <- results(DESeq_diet,
                          contrast = c("diet.ch1", "chow", "AIN76A")) %>% 
  na.omit() %>% 
  .[.$padj < 0.001 & (abs(.$log2FoldChange) > 1),]

  

ggo1 <- groupGO(gene     = rownames(sig_exp_genes),
                OrgDb    = dtb,
                keyType = "SYMBOL",
                ont      = "BP",
                level    = 1,
                readable = F)

ggo2 <- groupGO(gene     = rownames(sig_exp_genes),
                OrgDb    = dtb,
                keyType = "SYMBOL",
                ont      = "BP",
                level    = 2,
                readable = F)

ego <- enrichGO(gene          = rownames(sig_exp_genes),
                universe      = rownames(counts(DESeq_diet)),
                OrgDb         = dtb,
                keyType       = 'SYMBOL',
                ont           = "BP",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.005,
                qvalueCutoff  = 0.05,
                readable      = F)


df_ego<-as.data.frame(ego[,-8])

```

```{r process-count}
barplot(ego,
        showCategory = 20)
```

```{r process-graph}
goplot(ego)

```

### CNET plot

```{r gene-graph, fig.cap="Genes involved in cell porcesess"}
cnetplot(ego, categorySize = "pvalue", foldChange = rownames(sig_exp_genes))
```

### KEGG

```{r}
# search_kegg_organism('mmu', by='kegg_code')

sig_exp_genes$ENTREZID <- AnnotationDbi::mapIds(x = dtb,
                                                keys = rownames(sig_exp_genes),
                                                column = "ENTREZID",
                                                keytype = "ALIAS", # "SYMBOL", <-- SYMBOL uses exact matching. some Genes have updated names!
                                                multiVals = "first")
# sig_exp_genes <- sig_exp_genes %>% na.omit()
# keytypes(dtb) 

```

```{r}
kk <- enrichKEGG(gene          = sig_exp_genes$ENTREZID,
                 organism      = 'mmu',
                 pAdjustMethod = "BH",
                 qvalueCutoff  = 0.2,
                 pvalueCutoff  = 0.01)

kkres<-as.data.frame(kk@result)

significantkkres<-kkres[kkres$pvalue < kk@pvalueCutoff & kkres$p.adjust < kk@pvalueCutoff & kkres$qvalue < kk@qvalueCutoff,2,drop=F]

geneList<-sig_exp_genes$log2FoldChange
names(geneList)<- sig_exp_genes$ENTREZID

download.pathway<-function(keggid){
folder<-"pics"
if (!(folder %in% list.files())) {dir.create(folder)}
setwd(folder)
pic <- pathview(gene.data  = geneList,
                pathway.id = keggid,
                species    = stringr::str_extract(keggid,"[A-z]+"),
                limit      = list(gene=max(abs(geneList)), cpd=1))
setwd("..")
}

a <- lapply(rownames(significantkkres),download.pathway)

mkk <- enrichMKEGG(gene           = sig_exp_genes$ENTREZID,
                   organism       = 'mmu',
                   pAdjustMethod  = "BH",
                   qvalueCutoff   = 0.2,
                   pvalueCutoff   = 0.05)

# mkkres <- as.data.frame(mkk@result)
```

### KEGG images

<p><a class="btn btn-primary" data-toggle="collapse" href="#collapseExample4" role="button" aria-expanded="false" aria-controls="collapseExample4"> KEGG images </a></p>

::: {#collapseExample4 .collapse}
::: {.card .card-body}
```{r}
piclist <- list.files(path = "pics",
                      pattern = '*.png$',)
                      # pattern = '^[a-zA-Z0-9]*.png$',)

knitr::include_graphics(paste("pics", piclist, sep = "/"))
```
:::
:::

```{r Kegg-glycolysis, fig.cap="Graph of Glycolysis/ Gluconeogenesis"}
knitr::include_graphics(paste("pics", piclist[1], sep = "/"))
```

```{r Kegg-pentose, fig.cap="Graph of Pentose phosphate pathway"}
knitr::include_graphics(paste("pics", piclist[3], sep = "/"))
```

```{r Kegg-fructose, fig.cap="Graph of Fructose and mannose Metabolism"}
knitr::include_graphics(paste("pics", piclist[5], sep = "/"))
```

### BCV distance

```{r}
count_data <- as.data.frame(counts(dds_diet))
groups <- dds_diet@colData$diet.ch1
d <- DGEList(counts=count_data, group=groups)

cpm <- cpm(d)
keep <- rowSums(cpm>1) >= ncol(cpm)/2 # adjust for your dataset
# Here, a CPM value of 1 means that a gene is expressed if it has at least 20 counts (with a total of 20 million reads)
d <- d[keep, ]
d$samples$lib.size <- colSums(d$counts)
d <- calcNormFactors(d, method= "TMM")
```

```{r BCV-distance}
col = as.numeric(d$samples$group)
plotMDS(d, method="bcv",pch = 20,col = 1:4)
legend("bottomright",
       as.character(unique(d$samples$group)), col=1:4, pch=20)
```

### BCV Plot

```{r}
# Estimating the dispersion

d1 <- estimateCommonDisp(d, verbose=T)
d1 <- estimateTagwiseDisp(d1)
```

```{r BCV}
# names(d1)
plotBCV(d1)
```

```{r}
# unique(groups)

et12 <- exactTest(d1, pair=unique(groups)[1:2]) # Select chow and AIN76A

out <- topTags(et12, n = 10)

knitr::kable(out$table, 
             caption = paste("method: ", out$adjust.method,
             "\ncomparison: ", out$comparison, 
             "\ntest: ", out$test))

de1 <- decideTestsDGE(et12, adjust.method="BH", p.value=0.05)
summary(de1)

design <- model.matrix(~groups) 

y <- estimateDisp(d,design) 

#To perform quasi-likelihood F-tests: 
fit <- glmQLFit(y,design) 
qlf <- glmQLFTest(fit,coef=2)

out <- topTags(qlf)

knitr::kable(out$table, 
             caption = paste("method: ", out$adjust.method,
             "\ncomparison: ", out$comparison, 
             "\ntest: ", out$test))

```

```{r}
fit <- glmFit(y,design) 
lrt <- glmLRT(fit,coef=2) 

out <- topTags(lrt)

knitr::kable(out$table, 
             caption = paste("method: ", out$adjust.method,
             "\ncomparison: ", out$comparison, 
             "\ntest: ", out$test))
```

------------------------------------------------------------------------

# Interpretation

## Top genes

### PLA2G4C

[PLA2G4C](https://www.ncbi.nlm.nih.gov/gene/232889) gene encodes a protein belonging to the phospholipase A2 enzyme family. This protein acts to break down glycerophospholipids, producing free fatty acids and lysophospholipids, which are important for the production of signaling molecules. The protein is calcium-independent and is membrane-bound.

### RETNLB

[RETNLB](https://www.ncbi.nlm.nih.gov/gene/57263) gene encodes a protein called resistin-like beta (RETNLB). This protein is a member of the resistin-like molecule family and is involved in immune regulation and metabolic processes. It is secreted and may play a role in inflammation, insulin resistance, and adipocyte metabolism. Tissue is expressed only in the gastrointestinal tract, particularly the colon.

### G6PC

[G6PC](https://www.ncbi.nlm.nih.gov/gene/14377) gene provides instructions for making an enzyme called glucose-6-phosphatase, which plays a key role in sugar metabolism. Mutations in the G6PC gene can lead to several conditions, including glycogen storage disease type Ia (GSD Ia), also known as von Gierke disease, and type Ib (GSD Ib). These conditions affect the body's ability to store and release glucose properly, resulting in symptoms such as low blood sugar, enlarged liver, and delayed growth. This gene was included in a research "The absence of hepatic glucose-6 phosphatase/ ChREBP couple is incompatible with survival in mice". In this research, the researchers investigated the effects of deleting the ChREBP (carbohydrate response element-binding protein) gene in mice that already lacked the G6Pase (glucose-6 phosphatase) gene, which is essential for glucose production in the liver. The researchers found that the combined deletion of ChREBP and G6Pase led to a significant decrease in lipid accumulation in the liver, but resulted in exacerbated glycogen accumulation, causing hepatomegaly (enlarged liver) and liver damage. The study highlights the important role of the ChREBP-G6Pase duo in regulating glucose-6 phosphate (G6P) pathways in the liver, and suggests that further research is needed to understand the complex interactions between these genes and their impact on liver metabolism.[@2021]

### CBR3

[CBR3](https://www.ncbi.nlm.nih.gov/gene/109857/) encodes for an enzyme called carbonyl reductase 3, which is involved in the metabolism of various drugs and endogenous compounds in the body. The GeneCards entry provides information on the gene's basic details, including its location, aliases, and function. It also includes information on the gene's expression patterns, protein structure, and associated diseases or disorders.

### ANGPT4/ Ang4

[Ang4](https://www.ncbi.nlm.nih.gov/gene/219033) encodes for a protein called angiopoietin-4, which is involved in the regulation of blood vessel development and maintenance. The GeneCards entry provides information on the gene's basic details, such as its location, aliases, and function. It also includes information on the gene's expression patterns, protein structure, and associated diseases or disorders.

------------------------------------------------------------------------

The most expressed gene Pla2g4c (Figure \@ref(fig:topGenes)). When comparing the expression of the gene compared to the used feeding diet, the normalized count between chow and AIN76A is significantly different as seen in \@ref(fig:topG-count). The gene showed higher expression in samples fed with chow than other samples as seen in \@ref(fig:gene-diet-matrix). Beside Pla2g4c, the genes Cbr3, Ddah1, Ang4 and Retnlb show higher expression in mice fed with chow diet, while genes like Ifit3, Ifit1, E030010A14Rik, Aldob and G6pc show under expression compared to other feeds.

In figure \@ref(fig:volcanoplot) we compared chow and AIN76A feeds to produces a enhanced volcano plot. Aldob gene is under expressed while genes Ang4, Cbr3 and Retnlb are over expressed. The highest Log_10 value holds the gene Ang4, making it the most statistically significant gene. In comparison from the most significant gene using descending absolute value of log2Fold(\@ref(fig:topGenes)) Ang4 shows higher normalized count(Figure \@ref(fig:topG-count2)) in chow foods compared to Pla2g4c count(Figure \@ref(fig:topG-count)).

## Metabolic procesess

Pla2g4c and Ang4 genes are both involved in glycerolipid metabolic process(Figure \@ref(fig:gene-graph)). 
Pla2g4c shares the glycerophospholipid catabolic process with Pnliprp2 gene. 
Ang4 has been identified to be tied to increase of Tie2 and Akt phosphorylation[@2004]. 
Ang4, is produced by mouse Paneth cells, is secreted into the gut lumen and has bactericidal activity against intestinal microbes. Angiogenins have been implicated in tumor-associated angiogenesis. 
Ang4 expression is induced by *Bacteroides thetaiotaomicron*, a predominant member of the gut microflora, revealing a mechanism whereby intestinal commensal bacteria influence gut microbial ecology and shape innate immunity[@2003]. 
Over expression of Ang4 genes could possibly imply a correlation in diet choice and microbial ecology.
More study is needed.

The study advises more intense study of feeds used in testing.
This small sample shows that different use of feeds may influence the results of the studies conducted using said feeds.
The researchers advice more thorough checking and testing of feeds used in test mice, as they may influence the results of studies.



# TODO

-   <input type="checkbox" checked>add table DEGENES in Results tables</input>

-   <input type="checkbox" checked >don't use gender ones. (DIff exp anal)</input>

-   <input type="checkbox" checked >write which two gropsu compared</input>

-   <input type="checkbox" checked >insert table from results ( indicate how many genes were expressed, which p valjue as threashold)</input>

-   <input type="checkbox" checked >heatmap : select top 20 expr genes based on p-val or absolute log 2 change</input>

    -   <input type="checkbox" checked >MAJA select top 5 genes and search literature if there are any similar findings, if genes were already observed by some other reasearcher, in order to be inportant to different diets</input>

-   <input type="checkbox" >inerpretation of results : Gcel1 was already observed in study [2002] that its importatnt for metabolism of carbohydrates. for 5 genes and 5 bio. procesess (obtained w GO or KEGG).</input>

# References
