---
title: "Summary"
author: "Tilen Gimpelj, Maja Kovač"
date: "`r date()`"
output: 
  html_document: 
    toc: yes
    toc_float: TRUE
    code_folding: hide
  bibliography: reference.bib
csl: ieee-with-url.csl
link-citations: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,include=T,error=F,warning = F,message=F)
pkgs <- c("rlang","tidyverse","readxl","writexl","lubridate","stringr","esquisse","miniUI","pheatmap","RColorBrewer","hexbin","BiocManager","reshape2","ggnewscale","ggbeeswarm","kableExtra", "DT")
bioc_pkgs <- c("DESeq2","SummarizedExperiment","GEOquery","biomaRt","org.Hs.eg.db","org.Mm.eg.db","pathview","clusterProfiler","EnhancedVolcano","apeglm","genefilter","tximport","tximeta","GenomicFeatures","edgeR")

for (pkg in pkgs) {if (pkg %in% installed.packages()) {message(pkg," installed, loading...");library(pkg,character.only = T)} else {message(pkg," not instlled, installing...");install.packages(pkg,dependencies =T,quiet = T)}}
bmngr<-"BiocManager";
if (bmngr %in% installed.packages()) {library(bmngr,character.only = T)} else {install.packages(bmngr,dependencies =T,quiet = T)}
for (bpkg in bioc_pkgs) {if (bpkg %in% installed.packages()) {message(bpkg," installed, loading...");library(bpkg,character.only = T)} else {message(bpkg," not instlled, installing...");BiocManager::install(bpkg,update=T,ask=F)}}
```
<p>
  <a class="btn btn-primary" data-toggle="collapse" href="#collapseExample1" role="button" aria-expanded="false" aria-controls="collapseExample1">
    Environment
  </a>
</p>
<div class="collapse" id="collapseExample1">
  <div class="card card-body">
```{r, results='asis',echo=FALSE}
info <- sessionInfo()
datatable(data.frame(version = sapply(info$otherPkgs,FUN = \(x) {c(x$package,x$Version)}),
                        "Package_Manager" = sapply(info$otherPkgs,FUN = \(x){if (x$Package %in% bioc_pkgs){"BiocManager"} else {""}})),
          caption = info$R.version$version.string)

```
  </div>
</div>
# Intro
Summary of article "Effects of Diet Choice on Stem Cell Function Necessitate Clarity in Selection and Reporting"

```{r}
GEOaccN <- "GSE151498"
```

Geo Access number: ``r GEOaccN``

# Preparation of data

```{r}
gse1 <- getGEO(GEOaccN,GSEMatrix =TRUE)[[1]]
se1 <- as(gse1, "SummarizedExperiment")
if (!(GEOaccN %in% list.files())){ getGEOSuppFiles(GEOaccN)}

files <- list.files(GEOaccN,full.names=T)
df1<-read.table(files[1], skip=0, sep = "\t", header=TRUE) #, row.names = 1)
df2<-read.table(files[2], skip=0, sep = "\t", header=TRUE) #, row.names = 2)

datatable(df2)
```
Genes  in the dataset:
<p>
  <a class="btn btn-primary" data-toggle="collapse" href="#collapseExample2" role="button" aria-expanded="false" aria-controls="collapseExample2">
    Genes
  </a>
</p>
<div class="collapse" id="collapseExample2">
  <div class="card card-body">
```{r}
df2 %>%  
  group_by(geneNames) %>% 
  dplyr::count(geneNames)  %>% 
  rename(count = n, "Gene Name" = geneNames) %>% 
  datatable()  

```

</div></div>

```{r}
df2 %>%
  rename("GeneName"="geneNames") %>% 
  group_by(GeneName) %>% 
  summarize_if(is.numeric,sum) %>% 
  as.data.frame -> df2a

df2b<-df2a[,-1]
rownames(df2b)<-df2a[,1]

df2b%>%colnames
se1@colData%>%rownames
rownames(se1@colData)<-colnames(df2b)


se1@colData$characteristics_ch1.3<-factor(str_replace_all(se1@colData$characteristics_ch1.3, "[^A-Za-z0-9_]", "."))
# se1@colData$characteristics_ch1.3 %>% levels() %>% 
#   str_split("[^A-Za-z0-9]",n = 3) %>% 
#   lapply( \(x) {x[3]}) %>% 
#   str_split("[^A-Za-z0-9]") %>% 
#   lapply( \(x) {str_subset(x,".+")}) %>% 
#   apply( FUN = \(x) {str_c(x,".")})
#   
  

```

# TODO

- genes with the highest value
- genes with the lowest value

- include info on gender (only for visualization)
```{r}
se1@colData$characteristics_ch1.5

```

```{r}
se1@colData$characteristics_ch1.3
```




# TL;DR

Wenge Li and colleagues, the findings include:

- Diet choice can significantly affect stem cell function, including proliferation, differentiation, and senescence.

- Different types of diets, such as high-fat diets, low-calorie diets, and fasting, have different effects on stem cells.

- The effects of diet on stem cells are mediated by various mechanisms, such as oxidative stress, inflammation, and epigenetic changes.

- The choice of animal models and cell types used in stem cell research can also affect the interpretation of the results and the generalizability of the findings.

- The quality and clarity of reporting in scientific publications are crucial for facilitating reproducibility and transparency in stem cell research, especially regarding the details of diet selection and administration.
